---
title: "Documentation ts"
author: "Lena Bueschel"
date: "06/2022"
output: word_document
---

#Preperation - load packages
library(raster)
library(ncdf4)
library(sp)
library(rgdal)
library(tidyverse)
library(variables)
library(reshape2)
library(lubridate)
library(dplyr)
library(data.table)

#set working directory 
setwd("D:/LSG/Lena/IFPRI")


#1. EXTRACT SOILMOISTURE VALUES FOR CROPCUT LOCATIONS - ESA CCI DATASETS 
```{r}
#import dataset one acre fund for information about the cropcut locations
oneaf_DATA_final <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/CropCuts_1AF_finalselection.csv")
#get processed 1af file (export from 1st file)


for(y in 2016:2020){

  data <- filter(oneaf_DATA_final, year == y, field_latitude != 'NA', field_longitude != 'NA')
  
  #get coordinates and create dataframe
  coordinates_shp <- SpatialPointsDataFrame(data=data, coords=data[,c(7,6)], 
                                                         proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))

  #import netCDF files 
  ESA_CCI_files_prev <- list.files(paste0("D:/LSG/Lena/IFPRI/ESA_CCI_SM_v06.1/", y-1), full.names=T) 
  ESA_CCI_files_act <- list.files(paste0("D:/LSG/Lena/IFPRI/ESA_CCI_SM_v06.1/", y), full.names=T)   

  #combine netCDF files to also extract values from previous year 
  ESA_CCI_files_new <- c(ESA_CCI_files_prev, ESA_CCI_files_act)

  #setup dataframe for results
  results_soilmoist <- as.data.frame(matrix(nrow = length(ESA_CCI_files_new), ncol = length(coordinates_shp)))

  #name columns with ID_lena
  for (j in 1:length(coordinates_shp)) {
    colnames(results_soilmoist) <- c(data$ID)
  }


#create raster data & extract soilmoisture values
  for (i in 1:length(ESA_CCI_files_new)) {
    raster_ESA_CCI <- raster(ESA_CCI_files_new[i], varname = "sm")
    extract_results <- raster::extract(raster_ESA_CCI, coordinates_shp)
    results_soilmoist[i, 1:length(coordinates_shp)] <- extract_results
    if(i %in% seq(from = 50, to = NROW(ESA_CCI_files_new), by = 50)){ print(i)}
  }

  #name rows with date 
  for (l in 1:length(ESA_CCI_files_new)) {
    date <- basename(ESA_CCI_files_new[l])
    date2 <- substr(date, 39, 46)
    row.names(results_soilmoist)[l] <- date2
  }

#create table and export  
write.csv(results_soilmoist, paste0("D:/LSG/Lena/IFPRI/ESA_CCI_SM_v06.1/Export Survey2021/cc_maize/soilmoist_daily_",y,"_new.csv"))
}

test2 <- as.data.frame(fread("D:/LSG/Lena/IFPRI/ESA_CCI_SM_v06.1/Export Survey2021/cc_maize/soilmoist_daily_2020_new.csv"))
```


#2. EXTRACT PRECIPITATION VALUES FOR CROPCUT LOCATIONS - CHIRPS DATASETS
```{r}
#import OneAcreFund dataset
oneaf_DATA_final <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/CropCuts_1AF_finalselection.csv")

for(y in 2016:2020){
  
  #get data for year of interest 
  data <- filter(oneaf_DATA_final, year == y, field_latitude != 'NA', field_longitude != 'NA') 
  
  #get coordinates and create dataframe
  points <- SpatialPointsDataFrame(data=data, coords=data[,c(7,6)], 
                                    proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))

  #import tifFs for considered years -> CHANGE YEAR IN FILEPATHS 
  CHIRPS_p05_files_prev <- list.files(paste0("D:/LSG/Lena/IFPRI/CHIRPS p0.5/CHIRPS_p05_",y-1), full.names = T)
  CHIRPS_p05_files_act <- list.files(paste0("D:/LSG/Lena/IFPRI/CHIRPS p0.5/CHIRPS_p05_",y), full.names = T)

  #combine files to also get data from previous year
  CHIRPS_p05_files_new <- c(CHIRPS_p05_files_prev, CHIRPS_p05_files_act)
  
  #setup dataframe for extracted values for considered years
  results_prec <- as.data.frame(matrix(nrow = length(CHIRPS_p05_files_new), ncol = length(points)))

  #name columns with ID_new 
  for (i in 1:length(points)) {
    colnames(results_prec) <- c(data$ID)
  }
  
  #get tiffs for each day and extract value from data of considered year 
  for (i in 1:length(CHIRPS_p05_files_new)) {
    raster_CHIRPS_p05_new <- raster::raster(CHIRPS_p05_files_new[i])
    extract_results <- raster::extract(raster_CHIRPS_p05_new, points)
    results_prec[i, 1:length(points)] <- extract_results
    if (i %in% seq(from=50, to=NROW(CHIRPS_p05_files_new), by=50)) { print(i) }
  }
  
  for (l in 1:length(CHIRPS_p05_files_new)) {
    date <- basename(CHIRPS_p05_files_new[l])
    date2 <- substr(date, 13, 22)
    row.names(results_prec)[l] <- date2
  }

  #export dataframe 
  write.csv(results_prec, paste0("D:/LSG/Lena/IFPRI/CHIRPS p0.5/Export/precipitation_daily_",y,"_new.csv"))
  
}

```

#3. EXTRACT HOURLY VALUES FROM ERA5-SOILWATER FOR THE CONSIDERED YEARS + PREVIOUS YEARS 
```{r}
#import OneAcreFund dataset
oneaf_DATA_final <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/CropCuts_1AF_finalselection.csv")


for (y in 2020) {
  #get data for year of interest 
  data <- filter(oneaf_DATA_final, year == y, field_latitude != 'NA', field_longitude != 'NA')
  
  #get coordinates and create dataframe 
  points <- SpatialPointsDataFrame(data=data, coords=data[,c(7,6)], 
                                    proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))

  #import netcdf-files as raster stack 
  ERA5_VSWL1_prev <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/VSWL1_DATA/ECMWF-DAILY_ACCUMULATION_volumetric_soil_water_layer1_",y-1,".nc"),
                                  varname = "swvl1") 
  ERA5_VSWL1_act <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/VSWL1_DATA/ECMWF-DAILY_ACCUMULATION_volumetric_soil_water_layer1_",y,".nc"), 
                                  varname = "swvl1") 


  ERA_VSWL1_new <- raster::stack(ERA5_VSWL1_prev, ERA5_VSWL1_act)


  #extract values from raster brick from the considered year 
  points_data <- ERA_VSWL1_new %>%
    raster::extract(points, df=T)
  
  points_data <- cbind(points_data, points$ID)
  points_data$ID <- NULL
  n <- ncol(points_data)
  names(points_data)[n] <- "ID"

  #export of timeseries just for the considered year 
  write.csv(points_data, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export VSWL1/vswl1_hourly_",y,"_new.csv"), row.names = F)
}

test <- as.data.frame(fread("D:/LSG/Lena/IFPRI/ERA5_Land/Export VSWL1/vswl1_hourly_2020_new.csv"))


```

#4. EXTRACT DAILY MEAN FROM HOURLY SOILWATER DATA (ERA5)
```{r}
for(y in 2020){
  data <- as.data.frame(fread(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export VSWL1/vswl1_hourly_",y,"_new.csv")))
  data$V1 <- NULL

  n <- ncol(data)
  row.names(data) <- data[,n]
  data <- data[,-n]

  data_daily <- as.data.frame(matrix(ncol=(ncol(data)/24), nrow=nrow(data)))
  row.names(data_daily) <- row.names(data)

  for(i in 1:NROW(data))
  { for (j in 1:length(data_daily))
    { data_daily[i,j] <- mean(unlist(data[i, c(((j*24)-23):(j*24))]), na.rm = TRUE) }
    if (i %in% seq(from=50, to=NROW(data), by=50)) { print(i) } }
  
  names(data_daily) <- unique(substr(names(data),2,11))
  data_daily$ID <- row.names(data_daily)
  data_daily_melted <- reshape2::melt(data_daily, id.vars="ID")
  names(data_daily_melted)[2] <- "Date"
  
  data_daily_melted$Date <- as.Date(data_daily_melted$Date, format="%Y.%m.%d")

  #head(data_daily_melted)
  
  write.csv(data_daily_melted, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export VSWL1/vswl1_daily_",y,"_new.csv"), row.names = F)
}
test <- read.csv("D:/LSG/Lena/IFPRI/ERA5_Land/Export VSWL1/vswl1_daily_2020_new.csv")

which(is.na(test$value))

which(is.na(data_daily_melted$value))

```


#5. EXTRACT HOURLY VALUES FROM ERA5-AIR TEMPERATURE FOR THE CONSIDERED YEARS + PREVIOUS YEARS
```{r}
#import OneAcreFund dataset
oneaf_DATA_final <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/CropCuts_1AF_finalselection.csv")


for(y in 2016:2020){
 #get data for year of interest 
  data <- filter(oneaf_DATA_final, year == y, field_latitude != 'NA', field_longitude != 'NA')
  
  #get coordinates and create shapefiles for several years of Survey2021
  points <- SpatialPointsDataFrame(data=data, coords=data[,c(7,6)], 
                                    proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
  
  #import as raster stack
  ERA5_ST_prev <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/SURFACE_TEMP_DATA/ECMWF-DAILY_ACCUMULATION_air_temperature_",y-1,".nc"),
                                varname = "t2m") 
  ERA5_ST_act <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/SURFACE_TEMP_DATA/ECMWF-DAILY_ACCUMULATION_air_temperature_",y,".nc"),
                               varname = "t2m")
  
  ERA5_ST_new <- raster::stack(ERA5_ST_prev, ERA5_ST_act)
  
  #extract values from stack
  points_data <- ERA5_ST_new %>%
    raster::extract(points, df=T)
  
  points_data <- cbind(points_data, points$ID)
  points_data$ID <- NULL
  n <- ncol(points_data)
  names(points_data)[n] <- "ID"
  
  #extract values from raster brick from the considered year
  write.csv(points_data, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export SURFACE_TEMP/surface_temp_hourly_",y,"_new.csv"),row.names = F) 
}


```

#6. EXTRACT DAILY MEAN FROM HOURLY AIR-TEMP DATA (ERA5)
```{r}
for(y in 2016:2020){
  
  data <- as.data.frame(fread(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export SURFACE_TEMP/surface_temp_hourly_",y,"_new.csv")))
  data$V1 <- NULL

  n <- ncol(data)
  row.names(data) <- data[,n]
  data <- data[,-n]


  data <- data -273.15
  
  data_daily_mean <- as.data.frame(matrix(ncol=(ncol(data)/24), nrow=nrow(data)))
  row.names(data_daily_mean) <- row.names(data)
  
  data_daily_max <- as.data.frame(matrix(ncol=(ncol(data)/24), nrow=nrow(data)))
  row.names(data_daily_max) <- row.names(data)
  
  data_daily_min <- as.data.frame(matrix(ncol=(ncol(data)/24), nrow=nrow(data)))
  row.names(data_daily_min) <- row.names(data)
  
  for(i in 1:NROW(data))
  { for (j in 1:length(data_daily_mean))
  { data_daily_mean[i,j] <- mean(unlist(data[i, c(((j*24)-23):(j*24))]), na.rm = TRUE)
    data_daily_max[i,j] <- max(unlist(data[i, c(((j*24)-23):(j*24))]), na.rm = TRUE)
    data_daily_min[i,j] <- min(unlist(data[i, c(((j*24)-23):(j*24))]), na.rm = TRUE)}
    if (i %in% seq(from=50, to=NROW(data), by=50)) { print(i) } }
  
  names(data_daily_mean) <- unique(substr(names(data),2,11))
  data_daily_mean$ID <- row.names(data_daily_mean)
  data_daily_mean_melted <- reshape2::melt(data_daily_mean, id.vars="ID")
  names(data_daily_mean_melted)[2] <- "Date"
  
  names(data_daily_max) <- unique(substr(names(data),2,11))
  data_daily_max$ID <- row.names(data_daily_max)
  data_daily_max_melted <- reshape2::melt(data_daily_max, id.vars="ID")
  names(data_daily_max_melted)[2] <- "Date"
  
  names(data_daily_min) <- unique(substr(names(data),2,11))
  data_daily_min$ID <- row.names(data_daily_min)
  data_daily_min_melted <- reshape2::melt(data_daily_min, id.vars="ID")
  names(data_daily_min_melted)[2] <- "Date"
  
  data_daily_mean_melted$Date <- as.Date(data_daily_mean_melted$Date, format="%Y.%m.%d")
  data_daily_max_melted$Date <- as.Date(data_daily_max_melted$Date, format="%Y.%m.%d")
  data_daily_min_melted$Date <- as.Date(data_daily_min_melted$Date, format="%Y.%m.%d")
  
  which(is.na(data_daily_min_melted$value))
  
  #head(data_daily_melted)
  
  write.csv(data_daily_mean_melted, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export SURFACE_TEMP/surface_temp_daily_mean_",y,"_new.csv"),row.names = F) 
  write.csv(data_daily_max_melted, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export SURFACE_TEMP/surface_temp_daily_max_",y,"_new.csv"),row.names = F)
  write.csv(data_daily_min_melted, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export SURFACE_TEMP/surface_temp_daily_min_",y,"_new.csv"),row.names = F)
}

```


#8. EXTRACT HOURLY VALUES FROM ERA5-TOTAL PRECIPITATION FOR THE CONSIDERED YEARS + PREVIOUS YEARS
```{r}
#import OneAcreFund dataset
oneaf_DATA_final <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/CropCuts_1AF_finalselection.csv")


for(y in 2016:2020){
  #get data for year of interest 
  data <- filter(oneaf_DATA_final, year == y, field_latitude != 'NA', field_longitude != 'NA') 
  
  #get coordinates and create dataframe
  points <- SpatialPointsDataFrame(data=data, coords=data[,c(7,6)], 
                                    proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))


  #import files as rasterstack 
  ERA5_TOTPREC_prev <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/TOTAL_PRECIPITATION/ECMWF-DAILY_ACCUMULATION_lwe_thickness_of_precipitation_amount_",y-1,".nc"))
  ERA5_TOTPREC_act <- raster::stack(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/TOTAL_PRECIPITATION/ECMWF-DAILY_ACCUMULATION_lwe_thickness_of_precipitation_amount_",y,".nc")) 
  
  ERA5_TOTPREC_new <- raster::stack(ERA5_TOTPREC_prev, ERA5_TOTPREC_act)
  
  #extract values from raster stack from the considered year
  points_data <- ERA5_TOTPREC_new %>%
    raster::extract(points, df=T)
  
  points_data <- cbind(points_data, points$ID)
  points_data$ID <- NULL
  n <- ncol(points_data)
  names(points_data)[n] <- "ID"
  
  #expot values from the considered year
  write.csv(points_data, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export TOTAL_PREC/tp_hourly_",y,"_new.csv"), row.names = F)
}


```

#9. EXTRACT DAILY MEAN FROM HOURLY PRECIPITATION DATA (ERA5)
```{r}
for(y in 2016:2020){
  #get hourly data 
  data <- as.data.frame(fread(paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export TOTAL_PREC/tp_hourly_",y,"_new.csv")))
  data$V1 <- NULL
  
  n <- ncol(data)
  row.names(data) <- data[,n]
  data <- data[,-n]
  
  data <- data * 1000
  
  
  #setup new dataframe 
  data_daily <- as.data.frame(matrix(ncol=(ncol(data)/24), nrow = nrow(data)))
  row.names(data_daily) <- row.names(data)
  
  
  #loop 
  for(i in 1:NROW(data))
  { for (j in 1:length(data_daily))
  { data_daily[i,j] <- sum(unlist(data[i, c(((j*24)-23):(j*24))])) }
    if (i %in% seq(from=50, to=NROW(data), by=50)) { print(i) } }
  
  names(data_daily) <- unique(substr(names(data),2,11))
  data_daily$ID <- row.names(data_daily)
  data_daily_melted <- reshape2::melt(data_daily, id.vars="ID")
  names(data_daily_melted)[2] <- "Date"
  
  data_daily_melted$Date <- as.Date(data_daily_melted$Date, format="%Y.%m.%d")
  
  #export 
  write.csv(data_daily_melted, paste0("D:/LSG/Lena/IFPRI/ERA5_Land/Export TOTAL_PREC/tp_daily_",y,"_new.csv"),row.names = F) 
}

```

#9. COMPARISON MONTHLY SUM/MEAN OF ERA5 & CHIRPS PRECIPITATION for 2020
```{r}
#import data and select important columns
data <- read.csv("D:/LSG/Lena/IFPRI/GrowingSeasonData/climate_data_growseas_2020.csv")

data <- select(data, Date, DOY, ID, era_prec, chirps, year)

#get calender and join
calender <- readRDS("D:/LSG/Lena/IFPRI/R Code WS9/calendar_1901_2100.rds")
calender_new <- filter(calender, year == '2020')

data <- left_join(data, calender_new, by = "DOY")

#aggregate for monthly sum 
data_aggr_sum <- aggregate(cbind(era_prec, chirps) ~ ID + month_str, data = data, FUN = sum, na.rm = TRUE)

#aggregate for monthly mean
data_aggr_mean <- aggregate(cbind(era_prec, chirps) ~ ID + month_str, data = data, FUN = mean, na.rm = TRUE)

#get OneAcreFund data and join with sum/mean data 
cropcuts <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/final_data/One_Acre_Fund_Data_2021_cleaned.csv")
cropcuts_new <- filter(cropcuts, year == '2020')
cropcuts_new <- select(cropcuts_new, country, ID_lena)

names(cropcuts_new)[2] <- "ID"

data_sum <- left_join(data_aggr_sum, cropcuts_new, by = "ID")
data_mean <- left_join(data_aggr_mean, cropcuts_new, by = "ID")


#plot
ggplot(data_sum, aes(x = era_prec, y = chirps, color = country)) +
  geom_point() +
  labs(x = "ERA5-Precipitation [mm]", y= "CHIRPS-Precipitation [mm]", title = "Total monthly precipitation") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "right") +
  facet_wrap(~month_str)


ggplot(data_mean, aes(x = era_prec, y = chirps, color = country)) +
  geom_point() +
  labs(x = "ERA5-Precipitation [mm]", y= "CHIRPS-Precipitation [mm]", title = "Mean monthly precipitation") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "right") +
  facet_wrap(~month_str)
```

#10. COMPARING ESA & ERA5 SOILMOISTURE
```{r}
#import data and select important columns
data <- read.csv("D:/LSG/Lena/IFPRI/GrowingSeasonData/climate_data_growseas_complete.csv")

data <- select(data, Date, DOY, ID, era_vswl, esa_soilmoist)

#get OneAcreFund data and join with sum/mean data 
cropcuts <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/final_data/One_Acre_Fund_Data_2021_cleaned.csv")
cropcuts_new <- dplyr::select(cropcuts, country, ID_lena)

names(cropcuts_new)[2] <- "ID"

data_new <- left_join(data, cropcuts_new, by = "ID")

data_new$Date <- as.Date(data_new$Date)

#aggregate for daily mean 
data_new_aggr <- data_new %>% 
                    group_by(country, Date) %>%
                      summarise(era = mean(era_vswl, na.rm = TRUE),
                      esa = mean(esa_soilmoist, na.rm = TRUE), 
                      .groups = 'drop')

data_new_aggr$year <- substr(data_new_aggr$Date, 1, 4)

ggplot(data_new_aggr, aes(x = Date)) +
  geom_line(aes(y = era, color = "ERA5"), linetype = 1, lwd = 0.5) +
  geom_line(aes(y = esa, color = "ESA"), linetype = 1, lwd = 0.5) +
  labs(x = "Month", y= "Soilmoisture [m3m-3]", color = "Legend") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "right") +
  scale_x_date(date_labels = "%b") +
  facet_wrap(~country+year, scale = 'free_x') 

```
