---
title: "correlation"
author: "Lena Bueschel"
date: "07/2022"
output: word_document
---
library(tidyverse)
library(variables)
library(dplyr)
library(lubridate)
library(ggplot2)
library(GGally)
library(data.table)
library(ggpubr)

setwd("D:/LSG/Lena/IFPRI")


```{r}
#surveys with fertilizer
data_Neq <- read.csv("D:/LSG/Lena/IFPRI/OneAcreFund_DATASETS/final_selection_Neq_complete.csv")
data_Neq$DOY_plant <- yday(data_Neq$plant_date)

#divide into cluster 
cluster1 <- data_Neq[which((data_Neq$country%in%c("Rwanda", "Malawi", "Burundi"))&(data_Neq$DOY_plant>150)),]

cluster2 <- data_Neq[which((data_Neq$country== "Tanzania")|(data_Neq$country=="Kenya")|((data_Neq$country=="Rwanda")&(data_Neq$DOY_plant<150))),]

```

#Cluster 1 (every survey) - MAX 
```{r}
data_corr_cl1 <- select(cluster1, chirps_sum, esa_avg, era_temp_mean_avg, era_temp_min_avg, era_temp_max_avg, kdd_result, gs_length,
                      N_kg_ph, yield_kg_ph)
names(data_corr_cl1) <-  c("PREC", "SOILMOIST", "TAVG", "TMIN", "TMAX", "KDD", "GS_LENGTH", "N-EQ", "YIELD")

test <- round(cor(data_corr_cl1), 1)
test_plot <- ggcorrplot::ggcorrplot(test, type = "lower", lab = TRUE, colors = c("red", "white", "blue"), tl.cex = 18, lab_size = 6) +
              labs(title = "Cluster A") +
              theme(title = element_text(size = 20, hjust = 1), legend.title = element_text(size = 18), legend.text = element_text(size = 16))

```

#cluster 2 (every survey) - MAX
```{r}
data_corr_cl2 <- select(cluster2, chirps_sum, esa_avg, era_temp_mean_avg, era_temp_min_avg, era_temp_max_avg, kdd_result, gs_length,
                      N_kg_ph, yield_kg_ph)
names(data_corr_cl2) <-  c("PREC", "SOILMOIST", "TAVG", "TMIN", "TMAX", "KDD", "GS_LENGTH", "N-EQ", "YIELD")


test2 <- round(cor(data_corr_cl2), 1)
test_plot2 <- ggcorrplot::ggcorrplot(test2, type = "lower", lab = TRUE, colors = c("red", "white", "blue"), tl.cex = 18, lab_size = 6) +
              labs(title = "Cluster B") +
              theme(title = element_text(size = 20, hjust = 1),legend.title = element_text(size = 18), legend.text = element_text(size = 16))

plot_comb <- ggarrange(test_plot, test_plot2)

png("D:/LSG/Lena/IFPRI/corrplots_final/corr_max_comb_new.png", height = 600, width = 1000)
print(plot_comb)
dev.off()
```


#loop for every survey - Cluster 1 - MAX
```{r}
#select important data
data_corr_cl1 <- select(cluster1, survey, chirps_sum, esa_avg, era_temp_mean_avg, era_temp_min_avg, era_temp_max_avg, kdd_result, gs_length,
                    N_kg_ph, yield_kg_ph)

for(i in 1:length(unique(data_corr_cl1$survey))){
  data_corr_sel <- data_corr_cl1[which(data_corr_cl1$survey==unique(data_corr_cl1$survey)[i]),]
  names(data_corr_sel) <- c("survey", "PRCP_CHIRPS", "SM_ESACCI", "TAVG_ERA5","TMIN_ERA5", "TMAX_ERA5", "KDD_result", "GS_LENGTH",
                            "N-EQ", "YIELD")
  
  plot1 <- ggcorr(data_corr_sel[,c(2:10)], method = c("pairwise", "pearson"), label = TRUE, low = "red", mid = "white", high = "blue",
                  label_size = 6) +
    ggtitle(data_corr_sel$survey)
  
  png(paste0("D:/LSG/Lena/IFPRI/corrplots3/", data_corr_sel$survey[1], "cluster1.png"), height=1000, width=1000)
    print(plot1)
  dev.off()
}
```

#loop for every survey - Cluster 2 - MAX
```{r}
#select important data
data_corr_cl2 <- select(cluster2, survey, chirps_sum, esa_avg, era_temp_mean_avg, era_temp_min_avg, era_temp_max_avg, kdd_result, gs_length,
                    N_kg_ph, yield_kg_ph)

for(i in 1:length(unique(data_corr_cl2$survey))){
  data_corr_sel <- data_corr_cl2[which(data_corr_cl2$survey==unique(data_corr_cl2$survey)[i]),]
  names(data_corr_sel) <- c("survey", "PRCP_CHIRPS", "SM_ESACCI", "TAVG_ERA5","TMIN_ERA5", "TMAX_ERA5", "KDD_result", "GS_LENGTH",
                            "N-EQ", "YIELD")
  
  plot1 <- ggcorr(data_corr_sel[,c(2:10)], method = c("pairwise", "pearson"), label = TRUE, low = "red", mid = "white", high = "blue",
                  label_size = 6) +
    ggtitle(data_corr_sel$survey)
  
  png(paste0("D:/LSG/Lena/IFPRI/corrplots3/", data_corr_sel$survey[1], "_cluster2.png"), height=1000, width=1000)
    print(plot1)
  dev.off()
}
```

#Cluster 1 (every survey) - REDUCED
```{r}
data_corr_cl1 <- select(cluster1, chirps_sum, esa_avg, kdd_result, N_kg_ph, yield_kg_ph)
names(data_corr_cl1) <-  c("PREC", "SOILMOIST", "KDD", "N-EQ", "YIELD")

red_corr1 <- round(cor(data_corr_cl1),1)

plot_red1 <- ggcorrplot::ggcorrplot(red_corr1, type = "lower", lab = TRUE, colors = c("red", "white", "blue"), tl.cex = 18, lab_size = 6) +
              labs(title = "Cluster A") +
              theme(title = element_text(size = 20, hjust = 1),legend.title = element_text(size = 18), legend.text = element_text(size = 16))
```

#Cluster 2 (every survey) - REDUCED
```{r}
data_corr_cl2 <- select(cluster2, chirps_sum, esa_avg, kdd_result, N_kg_ph, yield_kg_ph)
names(data_corr_cl2) <-  c("PREC", "SOILMOIST", "KDD", "N-EQ", "YIELD")


red_corr2 <- round(cor(data_corr_cl2), 1)

plot_red2 <- ggcorrplot::ggcorrplot(red_corr2, type = "lower", lab = TRUE, colors = c("red", "white", "blue"), tl.cex = 18, lab_size = 6) +
              labs(title = "Cluster B") +
              theme(title = element_text(size = 20, hjust = 1),legend.title = element_text(size = 18), legend.text = element_text(size = 16))

plot_red_comb <- ggarrange(plot_red1, plot_red2)

png("D:/LSG/Lena/IFPRI/corrplots_final/corr_red_comb_new.png", height = 400, width = 800)
print(plot_red_comb)
dev.off()
```

#loop for every survey - Cluster 1 - REDUCED
```{r}
#select important data
data_corr_cl1 <- select(cluster1, survey, chirps_sum, esa_avg, kdd_result, N_kg_ph, yield_kg_ph)

for(i in 1:length(unique(data_corr_cl1$survey))){
  data_corr_sel <- data_corr_cl1[which(data_corr_cl1$survey==unique(data_corr_cl1$survey)[i]),]
  names(data_corr_sel) <- c("survey", "PRCP_CHIRPS", "SM_ESACCI", "KDD_result",
                            "N-EQ", "YIELD")
  
  plot1 <- ggcorr(data_corr_sel[,c(2:6)], method = c("pairwise", "pearson"), label = TRUE, low = "red", mid = "white", high = "blue", label_size = 6) +
    ggtitle(data_corr_sel$survey)
  
  png(paste0("D:/LSG/Lena/IFPRI/corrplots3/", data_corr_sel$survey[1], "_cluster1_red.png"), height=1000, width=1000)
    print(plot1)
  dev.off()
}
```

#loop for every survey - Cluster 2 - REDUCED
```{r}
#select important data
data_corr_cl2 <- select(cluster2, survey, chirps_sum, esa_avg, kdd_result, N_kg_ph, yield_kg_ph)

for(i in 1:length(unique(data_corr_cl2$survey))){
  data_corr_sel <- data_corr_cl2[which(data_corr_cl2$survey==unique(data_corr_cl2$survey)[i]),]
  names(data_corr_sel) <- c("survey", "PRCP_CHIRPS", "SM_ESACCI", "KDD_result",
                            "N-EQ", "YIELD")
  
  plot1 <- ggcorr(data_corr_sel[,c(2:6)], method = c("pairwise", "pearson"), label = TRUE, low = "red", mid = "white", high = "blue", label_size = 6) +
    ggtitle(data_corr_sel$survey)
  
  png(paste0("D:/LSG/Lena/IFPRI/corrplots3/", data_corr_sel$survey[1], "_cluster2_red.png"), height=1000, width=1000)
    print(plot1)
  dev.off()
}
```

